\begin{problem}[APMO]
	A positive integer is called \textit{fancy} if it can be expressed in the form $$2^{a_1}+2^{a_2}+ \cdots+ 2^{a_{100}},$$ where $a_1,a_2, \ldots, a_{100}$ are non-negative integers that are not necessarily distinct. Find the smallest positive integer $n$ such that no multiple of $n$ is a fancy number. \flushright \href{http://artofproblemsolving.com/community/c6h1243426p6362865}{Link}
\end{problem}


\begin{problem}[Argentina Intercollegiate Olympiad First Level]
	Find all positive integers $a,b,c,$ and $d$, all less than or equal to $6$, such that
	\begin{align*}
	\frac{a}{b} = \frac{c}{d} + 2.
	\end{align*}
\end{problem}



\begin{problem}[Argentina Intercollegiate Olympiad Third Level]
	Find a number with the following conditions:
	\begin{enumerate}
		\item it is a perfect square,
		\item when $100$ is added to the number, it equals a perfect square plus $1$, and
		\item when $100$ is again added to the number, the result is a perfect square.
	\end{enumerate}
\end{problem}




\begin{problem}[Austria Regional Competition]
	Determine all positive integers $k$ and $n$ satisfying the equation
	\begin{align*}
	k^2 - 2016 = 3^n.
	\end{align*}
\end{problem}



\begin{problem}[Azerbaijan TST]
	The set $A$ consists of positive integers which can be expressed as $2x^2+3y^2,$ where $x$ and $y$ are integers (not both zero at the same time).
	\begin{enumerate}
		\item Prove that there is no perfect square in $A$.
		\item Prove that the product of an odd number of elements of $A$ cannot be a perfect square.
	\end{enumerate}
	\flushright \href{http://artofproblemsolving.com/community/c6h1201200p5906668}{Link}
\end{problem}


\begin{problem}[Baltic Way]
	For which integers $n = 1,2,\ldots, 6$ does the equation \[a^n + b^n = c^n + n\] have a solution in integers? \hfill \href{https://artofproblemsolving.com/community/c6h1334536p7212068}{Link}
\end{problem}

\begin{problem}[Bay Area Olympiad]
	Find a positive integer $N$ and $a_1, a_2, \ldots, a_N$, where $a_k \in \{1, -1\}$ for each $k=1,2,\ldots,N$, such that \[a_1 \cdot 1^3 + a_2 \cdot 2^3 + a_3 \cdot 3^3 + \cdots + a_N \cdot N^3 = 20162016,\] or show that this is impossible. \hfill \href{http://artofproblemsolving.com/community/c6h1203525p5929703}{Link}
\end{problem}



\begin{problem}[Belgium National Olympiad Final Round]
	Solve the equation
	\begin{align*}
	2^{2m+1}+9\cdot 2^m+5=n^2
	\end{align*}
	for integers $m$ and $n$.
\end{problem}


\begin{problem}[Bosnia and Herzegovina TST]
	Determine the largest positive integer $n$ which cannot be written as the sum of three numbers bigger than $1$ which are pairwise coprime. \hfill \href{http://artofproblemsolving.com/community/c6h1243220p6360359}{Link}
\end{problem}



\begin{problem}[Bulgaria National Olympiad]
	Determine whether there exists a positive integer $n<10^9$ such that $n$ can be expressed as a sum of three squares of positive integers in more than $1000$ distinct ways.
\end{problem}

