


\begin{problem}[Austria National Competition Final Round]
	Let $a,b$, and $c$ be integers such that
		\begin{align*}
			\frac{ab}{c} + \frac{ac}{b} + \frac{bc}{a}
		\end{align*}
	is an integer. Prove that each of the numbers
		\begin{align*}
			\frac{ab}{c} , \frac{ac}{b}, \text{ and } \frac{bc}{a}
		\end{align*}
	is an integer.
\end{problem}


\begin{problem}[Azerbaijan Balkan Math Olympiad Third TST] \label{azerbaijan2016}
	Find all natural numbers $n$ for which there exist primes $p$ and $q$ such that the following conditions are satisfied:
	\begin{enumerate}
		\item $p+2=q$, and
		\item $2^n+p$ and $2^n+q$ are both primes.
	\end{enumerate}
	\hfill \href{https://artofproblemsolving.com/community/c6h1323462p7131461}{Link}
\end{problem}


\begin{problem}[Azerbaijan Junior Mathematical Olympiad]
	Given  
	\begin{align*}
	34!=295232799039a041408476186096435b0000000,
	\end{align*}
	in decimal representation, find the numbers $a$ and $b$. \hfill \href{http://artofproblemsolving.com/community/c6h1195518p5852632}{Link}
\end{problem}


\begin{problem}[Azerbaijan Junior Mathematical Olympiad]
	A quadruple $(p,a,b,c)$ of positive integers is called a \textit{good quadruple} if 
	\begin{enumerate}[(a)]
		\item $p $ is an odd prime,
		\item $a,b$, and $c $ are distinct,
		\item $ab+1,bc+1$, and $ca+1$ are divisible by $p$.
	\end{enumerate}
	Prove that for all good quadruples $(p,a,b,c)$, \[p+2\le \frac {a+b+c}{3} ,\] and show the equality case. \flushright \href{http://artofproblemsolving.com/community/c6h1195523p5852672}{Link}
\end{problem}


\begin{problem}[Balkan]
	Find all monic polynomials $f$ with integer coefficients satisfying the following condition: there exists a positive integer $N$ such that $p$ divides $2(f(p)!)+1$ for every prime $p>N$ for which $f(p)$ is a positive integer.
	\\
	\textbf{Note.} A monic polynomial has a leading coefficient equal to $1$. \hfill \href{http://artofproblemsolving.com/community/c6h1239091p6316984}{Link}
\end{problem}


\begin{problem}[Baltic Way]
	Let $n$ be a positive integer and let $a, b, c, d$ be integers such that $n | a + b + c + d$ and $n | a^2 + b^2 + c^2 + d^2. $
	Show that \[n | a^4 + b^4 + c^4 + d^4 + 4abcd.\]
	\hfill \href{https://artofproblemsolving.com/community/c6h1334537p7212083}{Link}
\end{problem}

	
\begin{problem}[Bay Area Olympiad]
	The distinct prime factors of an integer are its prime factors listed without repetition. For example, the distinct prime factors of $40$ are $2$ and $5$. Let $A=2^k - 2$ and $B= 2^k \cdot A$, where $k$ is an integer ($k \geq 2$).
	Show that for every integer $k$ greater than or equal to $2$,
	\begin{enumerate}
		\item $A$ and $B$ have the same set of distinct prime factors, and
		\item $A+1$ and $B+1$ have the same set of distinct prime factors.
	\end{enumerate}
	\flushright \href{http://artofproblemsolving.com/community/c6h1203225p5926002}{Link}
\end{problem}



\begin{problem}[Belgium Flanders Math Olympiad Final Round]
	Find the smallest positive integer $n$ which does not divide $2016!$.
\end{problem}




\begin{problem}[Benelux]
	Find the greatest positive integer $N$ with the following property: there exist integers $x_1, x_2, \ldots, x_N$ such that $x^2_i - x_ix_j$ is not divisible by $1111$ for any $i\ne j.$ \hfill \href{http://artofproblemsolving.com/community/c6h1236281p6284414}{Link}
\end{problem}



\begin{problem}[Bulgaria National Olympiad]
	Find all positive integers $m$ and $n$ such that \[\left(2^{2^m}+1\right)\left(2^{2^n}+1\right)\] is divisible by $mn$.
\end{problem}

